Implications of afforestation policies for global markets

### 2024-02-28 paper.Rmd
Update paper.Rmd

---
title: "Implications of afforestation policies for global markets"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Eric C. Davis, Maros Ivanic, and Brent Sohngen"
output: 
  bookdown::pdf_document2:
    keep_tex: TRUE
toc: FALSE
bibliography: references.bib
header-includes:
    - \usepackage{setspace}\doublespacing
abstract: "The projected growth of the population and incomes as implied by various shared socioeconomic pathways is expected to create pressures on converting forests into farmland as food prices increase. Depending on the specific path taken, SSP1 through SSP5, and the continuation of the current trends in agricultural productivity growth, the market impacts are expected to vary but generally result in increases in food prices. Policies aimed at reversing the deforestation trend by afforesting cropland would result in severe negative market impacts such as  higher food prices, especially in low agricultural productivity/high population growth scenarios."
---

@@

>>>>

---
title: "Implications of afforestation policies for global markets"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Eric C. Davis, Maros Ivanic, and Brent Sohngen"
output: 
  bookdown::pdf_document2:
    keep_tex: TRUE
toc: FALSE
bibliography: references.bib
header-includes:
    - \usepackage{setspace}\doublespacing
abstract: "The projected growth in population and incomes as implied by various shared socioeconomic pathways is expected to create pressure to convert forestland into farmland. At the same time, the increasingly negative climate impacts are expected to generate increasing pressure to enhance the terrestrial carbon sink. These goals seem incompatible as reversing the deforestation trend by afforesting cropland might result in negative market impacts such as higher food prices, especially in low agricultural productivity/high population growth scenarios. In order to better grasp the interrelationship and the magnitude of harm that might be caused by prioritizing the goal of mitigating deforestation, this analysis connects two respected global economic models: the Global Trade Analysis Project (GTAP) model and the Global Timber Model (GTM). "
---

@@

# Acknowledgements

The findings and conclusions in this publication are those of the author(s) and should not be construed to represent any official USDA or U.S. Government determination or policy.

# Funding statement

This research was supported [in part] by the U.S. Department of Agriculture, Economic Research Service.
